### 2014-12-09 Draft/abstract.tex
Dr. Xie's cmnts on Abstract, Intro, and Conclusion

Temporal constraints of an Application Programming Interface (API)
are the allowed sequences of method invocations in the API.
These constraints govern the secure and robust operation of client software using the API.
However, in practice, most API do not have formal temporal constraints.
In contrast, these constraints are typically described
informally in natural language API documents, and therefore are not amenable
to existing tools for checking formal temporal constraints.
\textit{The goal of this work is to assist developers to construct API clients that comply with 
temporal constraints of the API through the inference and formalization of these constraints found in natural language API documents.}
Since API documents are often verbose, manually identifying and writing formal temporal constraints can be prohibitively time-consuming and error-prone.
To address this issue,
we propose \tool: an approach based on Machine Learning (ML) and Natural Language Processing (NLP) for identifying and inferring formal temporal constraints.
To evaluate our approach, we apply \tool\ to infer and formalize temporal
constraints from \amazonAPI, \paypalAPI\ and the \CodeIn{java.io} package in the
JDK API.
Our results indicate that \tool\ is effective in identifying temporal
constraint sentences (from over
4000 human-annotated API sentences) with the average precision, recall, and F-score
of 79.0\%, 60.0\%, and 65.0\%, respectively.
Furthermore, our evaluation also demonstrate that \tool\ achieves an accuracy of 70\% in inferring and formalizing 77 temporal constraints from these temporal constraint sentences.

>>>>

Temporal constraints of an Application Programming Interface (API)
are the allowed sequences of method invocations in the API.
These constraints govern the secure and robust operation of client software using the API.
However, in practice, most APIs do not come with formal temporal constraints.
In contrast, these constraints are typically described
informally in natural language API documents, and therefore are not amenable
to existing tools for checking formal temporal constraints.
\textit{The goal of this work is to assist developers to construct API clients that comply with 
temporal constraints of the API through the inference and formalization of these constraints found in natural language API documents.}
Since API documents are often verbose, manually identifying and writing formal temporal constraints can be prohibitively time-consuming and error-prone.
To address this issue,
we propose \tool: an approach based on Machine Learning (ML) and Natural Language Processing (NLP) for identifying and inferring formal temporal constraints.
To evaluate our approach, we apply \tool\ to infer and formalize temporal
constraints from the \amazonAPI, the \paypalAPI\, and the \CodeIn{java.io} package in the
JDK API.
Our results indicate that \tool\ is effective in identifying temporal
constraint sentences (from over
4000 human-annotated API sentences) with the average precision, recall, and F-score
of 79.0\%, 60.0\%, and 65.0\%, respectively.
Furthermore, our evaluation also demonstrates that \tool\ achieves an accuracy of 70\% in inferring and formalizing 77 temporal constraints from these temporal constraint sentences.

### 2014-12-09 Draft/conclusion.tex
Laurie's comments
Dr. Xie's cmnts on Abstract, Intro, and Conclusion

Despite being highly desirable, most APIs are not equipped with formal temporal constraints.
In contrast, documentation of API methods contains detailed specifications of temporal constraints in natural language text.
Manually writing formal specifications based on natural language text in API documents is prohibitively time consuming and error prone.
To address this issue, we have proposed a novel approach called \tool\ to infer temporal constraints from natural language text of API documents.
We applied \tool\ to infer temporal constraints from
\paypalAPI, \amazonAPI, and  
commonly used package \CodeIn{java.io} in the JDK API.
Our evaluation results show that \tool\ effectively identifies sentences describing
temporal constraints with an average 79\% precision and 60\% recall,
from more than 4000 sentences in subject API documents.
Furthermore, \tool\ also achieved an accuracy of
70\% in inferring 77 formal temporal constraints from these sentences.

>>>>

Despite being highly desirable, formal temporal constraints are missing from most APIs.
In contrast, documentation of API methods contains detailed specifications of temporal constraints in natural language text.
Manually writing formal specifications based on natural language text in API documents is prohibitively time-consuming and error-prone.
To address this issue, we have proposed a novel approach called \tool\ to infer temporal constraints from natural language text of API documents.
We applied \tool\ to infer temporal constraints from
the \paypalAPI, the \amazonAPI, and the 
commonly used package \CodeIn{java.io} in the JDK API.
Our evaluation results show that \tool\ effectively identifies sentences describing
temporal constraints with an average 79\% precision and 60\% recall,
from more than 4000 sentences in subject API documents.
Furthermore, \tool\ also achieved an accuracy of
70\% in inferring 77 formal temporal constraints from these temporal constraint sentences.

### 2014-12-09 Draft/introduction.tex
Dr. Xie's cmnts on Abstract, Intro, and Conclusion

Application Programming Interfaces (APIs) facilitates software reuse
by providing standardized mechanism to access API components.
However, APIs have some constraints governing the proper use of the API that must be followed.
One such type of constraints are temporal constraints [2], which are the allowed sequences of invocations of methods from the API.
Non-compliance to such constraints will often result in faulty applications that are unreliable to use and may even result in financial losses.

Formal analysis tools, such as model checker and runtime verifiers 
can assist in detection of the violations of the temporal constraints
in API clients as defects~\cite{lee2012towards}.
These tools typically accept formal representation of the temporal constraints for detecting violations.
However, temporal constraints are typically described in natural language text of API documents.
Such documents are provided to client-code developers through an online access, or are shipped with the API code.
For a method under consideration, API document may describe both the constraints on the method parameters
as well as the temporal constraints in terms of other methods that must be invoked pre/post invoking that method.
%We observe that a non-trivial portion (roughly 12\%) of the sentences (constraint-describing sentences)
%in \amazonAPI\ documentation describe temporal constraints.

Although natural language API description can be manually converted into formal constraints,
manually identifying and writing formal constraints based on natural language text in API documents can be prohibitively time-consuming and error-prone~\cite{wu2013inferring,RubingerWEB10}. 
%For instance, Wu et al.~\cite{wu2013inferring} report that it took one person ten hours to browse the documentation of one method from a web API, even before the person attempted to formalize the constraints on the method. 
For instance, the PDF version of the documentation for \amazonAPI\footnote{{\small \url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}}} spans 278 pages describing 51 methods.

@@

For instance, consider the sentences from \paypalAPI:
1) ``\textit{Use this call to complete a payment.}'' from \CodeIn{execute payment} method.
2) ``\textit{Use this call to refund a completed payment.}'' from \CodeIn{refund sale} method.
Sentence 1 is a descriptive statement about complete payment method.
In contrast, Sentence 1 indicates the temporal constraint that a payment must be completed before the refund call is initiated.
Since these sentences are not significantly different in terms of words, a simple keyword-based search will fail to distinguish between the two. 
Another problem with keyword-based search is that the method names (and synonyms) are part of the keywords themselves, thus resulting in a large number of keywords to be searched.
The large number of keywords further negatively affects accuracy.

Even after a sentence has been identified as a constraint sentence, an approach has to infer the references to the method in the sentences, which may often not be implicit. Consider Sentence 2 in preceding paragraph. The phrase \textit{``completed payment''} refers to the \CodeIn{execute payment} method in the API.

@@

A ML based approach for identifying the temporal constraint sentences addresses the limitations of keyword-based search by automatically learning patterns of temporal constraint sentences.
Furthermore, we propose to use a combination of words, syntax (parts of speech) of a sentence, and semantics (relationship between words) of a sentence as the features for learning patterns.
This combination allows \tool\ to make a finer grained distinction between the example sentences described earlier.
Furthermore, to identify the phrases as implicit method-invocation references, we propose to leverage domain dictionaries that are systematically created from API documents and generic English dictionaries.

In summary, the \tool\ approach leverages natural language description of API's to infer temporal constraints of method invocations.
As our approach analyzes API documents in natural language, it can be reused independent of the programming language of an API library.
Additionally, our approach complements existing mining-based approaches~\cite{buse2012synthesizing, thummalapenta07parseweb, Wang:2013:MSR, Zhong:2009:MMR} that partially address the problem by mining for common usage patterns among client code reusing the API.
Our results indicate that \tool\ is effective in identifying temporal
constraint sentences (from over
4000 human-annotated API sentences) with the average precision, recall, and F-score
of 79.0\%, 60.0\%, and 65.0\%, respectively.
Furthermore, our evaluation also demonstrate that \tool\ achieves an accuracy of 70\% in inferring 77 formal temporal constraints from these sentences.
This paper makes the following main contributions:

\begin{itemize}
	\item An ML and NLP-based approach that effectively infers formal temporal constraints of method invocations. 
	%To the best of our knowledge, our approach is the first one to apply NLP for inferring temporal constraints from API documents.
	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03}, which is a natural language parser to derive the grammatical structure of sentences.
	An open source implementation of the prototype is publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}, along with the experimental subjects and the results. 
	\item An evaluation of our approach on \amazonAPI, \paypalAPI, and commonly used package \CodeIn{java.io} from the JDK API. 
\end{itemize}

>>>>

Application Programming Interfaces (APIs) facilitates software reuse
by providing standardized mechanism to access API components.
However, an API has some constraints governing the proper use of the API that must be followed.
One such type of constraints are temporal constraints [2], which are the allowed sequences of invocations of methods from the API.
Non-compliance to such constraints will often result in faulty applications that are unreliable to use. % and may even result in financial losses.

Formal analysis tools, such as model checkers and runtime verifiers 
can assist in detecting violations of the temporal constraints
in API clients as defects~\cite{lee2012towards}.
These tools typically accept formal representation of the temporal constraints for detecting violations.
However, temporal constraints are typically described in natural language text of API documents.
Such documents are provided to client-code developers through an online access, or are shipped with the API code.
For a method under consideration, API document may describe both the constraints on the method parameters
as well as the temporal constraints in terms of other methods that must be invoked pre/post invoking that method.
%We observe that a non-trivial portion (roughly 12\%) of the sentences (constraint-describing sentences)
%in \amazonAPI\ documentation describe temporal constraints.

Although natural language API descriptions can be manually converted to formal constraints,
manually identifying and writing formal constraints based on natural language text in API documents can be prohibitively time-consuming and error-prone~\cite{wu2013inferring,RubingerWEB10}. 
%For instance, Wu et al.~\cite{wu2013inferring} report that it took one person ten hours to browse the documentation of one method from a web API, even before the person attempted to formalize the constraints on the method. 
For instance, the PDF version of the documentation for \amazonAPI\footnote{{\small \url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}}} spans 278 pages describing 51 methods.

@@

For instance, consider the sentences from the \paypalAPI:
1) ``\textit{Use this call to complete a payment.}'' from the \CodeIn{execute payment} method.
2) ``\textit{Use this call to refund a completed payment.}'' from the \CodeIn{refund sale} method.
Sentence 1 is a descriptive statement about the \CodeIn{execute payment} method.
In contrast, Sentence 2 indicates the temporal constraint that a payment must be completed before the refund call is initiated.
Since these sentences are not significantly different in terms of words, a simple keyword-based search will fail to distinguish between the two. 
Another problem with keyword-based search is that the method names (and synonyms) are part of the keywords themselves, thus resulting in a large number of keywords to be searched.
The large number of keywords further negatively affects accuracy.

Even after a sentence has been identified as a constraint sentence, an approach has to infer the references to the method in the sentences, which often may not be explicit. Consider Sentence 2 in the preceding paragraph. The phrase \textit{``completed payment''} refers to the \CodeIn{execute payment} method in the API.

@@

An ML based approach for identifying the temporal constraint sentences addresses the limitations of keyword-based search by automatically learning patterns of temporal constraint sentences.
Furthermore, we propose to use a combination of words, syntax (parts of speech) of a sentence, and semantics (relationship between words) of a sentence as the features for learning patterns.
This combination allows \tool\ to make a finer grained distinction between the example sentences described earlier.
Furthermore, to identify the phrases as implicit method-invocation references, we propose to leverage domain dictionaries that are systematically created from API documents and generic English dictionaries.

In summary, the \tool\ approach leverages natural language description of an API to infer temporal constraints of method invocations.
As our approach analyzes API documents in natural language, it can be reused independent of the programming language of an API library.
Additionally, our approach complements existing mining-based approaches~\cite{buse2012synthesizing, thummalapenta07parseweb, Wang:2013:MSR, Zhong:2009:MMR} that partially address the problem by mining for common usage patterns among client code reusing the API.
Our results indicate that \tool\ is effective in identifying temporal
constraint sentences (from over
4000 human-annotated API sentences) with the average precision, recall, and F-score
of 79.0\%, 60.0\%, and 65.0\%, respectively.
Furthermore, our evaluation also demonstrates that \tool\ achieves an accuracy of 70\% in inferring 77 formal temporal constraints from these sentences.
This paper makes the following main contributions:

\begin{itemize}
	\item An ML and NLP-based approach that effectively infers formal temporal constraints of method invocations. 
	%To the best of our knowledge, our approach is the first one to apply NLP for inferring temporal constraints from API documents.
	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03}, which is a natural language parser to derive the grammatical structure of sentences.
	An open source implementation of the prototype is publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}, along with the experimental subjects and the results. 
	\item An evaluation of our approach on the \amazonAPI, the \paypalAPI, and the commonly used package \CodeIn{java.io} from the JDK API. 
\end{itemize}
